---
title: "Practical Machine Learning Project"
author: "Amit Nagar"
date: "Sunday, December 07, 2014"
output: html_document
---

```{r echo=FALSE}
setwd("C:\\Users\\I013285\\Documents\\Amit\\CourseraR\\PML\\project")
library(caret)
require(leaps)
require(MASS)
library(forecast)
library(randomForest)
```

Read exercise data
```{r echo=TRUE}
pmlData<-read.table(file="pml-training.csv",header=TRUE, sep=",")
```

Data cleanup: Remove some of the columns that are not relevant for prediction.  Also, remove columns with NA values
```{r}
pmlTrain1<-subset(pmlData,,-c(X, user_name, raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp,new_window, num_window))

pmlTrain2<-pmlTrain1[, apply(pmlTrain1, 2, function(x) !any(is.na(x)))]
```


Now we will partition data into smaller sets
```{r echo=FALSE}
inTrain<-createDataPartition(y=pmlTrain2$classe,p=0.7,list=FALSE)

pmlTrain<-pmlTrain2[inTrain,]

pmlTest<-pmlTrain2[-inTrain,]
```

Preprocess - Standardize Variables
```{r echo=TRUE}
preObj<-preProcess(pmlTrain[,-53],method=c("center","scale"))
```

Estimate the out of sample error
```{r echo=TRUE}
outOfSampleErrorEstimate <- rfcv(trainx = pmlTrain[,-53], trainy = pmlTrain[,53], step=0.7)
```

The Out of Sample estimated error will be:
```{r echo=FALSE}
outOfSampleErrorEstimate[[2]]
```


Apply RandomForest to pmlTrain3 dataset
```{r echo=TRUE}
modelFit <- train(classe~.,data=pmlTrain, preProcess=c("center","scale"),method="rf")
print(modelFit)
```

```{r echo=TRUE}
testModel<-predict(modelFit,pmlTest)
```

##Generate predictions with the Test data

```{r echo=TRUE}
pmlRealTestData<-read.table(file="pml-testing.csv",header=TRUE, sep=",")

prediction <-predict(modelFit,pmlRealTestData)

print(prediction)

```


